\documentclass[10pt,a4paper,twoside,twocolumn]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage{gwa}
\usepackage{graphicx}
\usepackage{url}

\usepackage{listings} 
\usepackage{stfloats}

\newcommand{\eg}{e.\,g., }
\newcommand{\ie}{i.\,e., }
\def\lqq{\lq\lq}
\def\rqq{\rq\rq}
\def\dq#1{\lqq #1\rqq}
\def\zitat#1{\lqq \emph{#1}\rqq}

\begin{document}

\title{Distributed Version Control with Git}

\author{
  \authN{Richard Plangger, Simon Zünd and Klaus Nigsch}\\
  \matNr{1025637, 1025990, 1025991} \\
%  \kennZ{182, 182, 182}\\
  \authI{Institute of Computer Engineering}\\
  \authU{Vienna University of Technology}\\
  \email{e\{1025637,1025990,1025991\}@student.tuwien.ac.at}
}

\maketitle

% abstract
\abstract {
This paper explains what Distributed Version Control means. There are systems managing the work of content on many computers distributed over the network. It is described how and why they are used. Furthermore there are also sections which compare the most popular Distributed Version Control Systems, hopefully making a bit more clear which one to choose. The paper also picks out one of these, namely Git and goes into further detail explaining the use with the most frequently used commands and clarifying why Git is so popular these days. This paper will clarify, why Distributed Version Control Systems became so popular and what advantages they can bring into a programmer's daily work.

Distributed Version Control systems enable people to work on the same project, at the same time in different locations. We will not only describe how and why they are used, but also compare the most popular Distributed Version Control Systems against each other and show how they differ from centralized systems. The second part of the paper will describe Git, a system developed by Linus Torvalds to handle the source code of the linux kernel. We will explain the most important commands and give some technical background information. This paper will clarify, why Distributed Version Control Systems became so popular and what advantages they can bring into a programmer's daily work.
}

% - Introduction
\input{introduction}

\input{whyrevisioncontrol}

% -
\input{dvcshistory}

% - General description DCVS (Properties)
		
		
		
% - A brief history of DCVS (Klaus)

% - Begriffserklärung (Simon)
\input{explanation_of_terms}

%	- Changing of Workflows (Simon)
\input{changeofworkflows}

%	- Critism on Distributed Version Control Systems (Klaus)
\input{critism_on_dvcs}



% GIT
  %   +-- History
  \input{githistory}
  %   +-- How does git work
  \input{how_does_git_work}
  %   +-- Comparison to other DVCS
  \input{comparison_to_other_dvcs}
  %   +-- Current Development. How uses git?
  \input{current_development}

% Conclusion
\input{conclusion}

% References
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
